Something About Ground Based Asteroseismology

### 2017-09-18 paper/aldebaran.tex
breakthrough
pope affiliations

\author[0000-0003-2595-9114]{Benjamin Pope}
\affiliation{Sydney Institute for Astronomy, School of Physics, University of Sydney, Sydney NSW 2006, Australia} % for the moment - if it is a couple of months til this is published I should say NYU

@@

BP is grateful for funding from the Breakthrough Foundation. % possibly update to say Sagan

>>>>

\author[0000-0003-2595-9114]{Benjamin Pope}
\affiliation{Sydney Institute for Astronomy, School of Physics, University of Sydney, Sydney NSW 2006, Australia} % for the moment - if it is a couple of months til this is published I should say NYU
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003, USA}
\affiliation{NASA Sagan Fellow}

@@

BP is grateful for funding from the Breakthrough Prize Foundation. This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute.
 % possibly update to say Sagan
